\chapter{The divine help of All\=ah} 

\textvtt{
There are many reasons for which the divine help of All\=ah comes down to His servants. But here I'll mention the most important five reasons (according to my understanding) for getting All\=ah's divine help at the time of calamity. They are all from the \textit{Kit\=ab} and the \textit{Sunnah}.

\section*{The First Requirement: True Belief}
All\=ah \textit{rabbul 'izzah} says,
}
\begin{center}
    \begin{RLtext}
            وَكَانَ حَقًّا عَلَيْنَا نَصْرُ ٱلْمُؤْمِنِينَ 
    \end{RLtext}
    \textbf{And (it is a duty) incumbent upon Us was to support (help) the believers.} [30:47]
\end{center}
\textvtt{
Hence the first requirement to attain the help of All\=ah \textit{rabbul 'izzah} is to be (true) believers. Then what is believe (\textit{\=im\=an})? The Had\=ith of \textit{Jibril} peace be upon him we know the definition or the articles of belief (\textit{\=im\=an}),
}
\begin{RLtext}
    عَنْ عُمَرَ رَضِيَ اللهُ عَنْهُ أَيْضًا قَالَ:\\
    بَيْنَمَا نَحْنُ جُلُوسٌ عِنْدَ رَسُولِ اللَّهِ صلى الله عليه و سلم ذَاتَ يَوْمٍ، إذْ طَلَعَ عَلَيْنَا رَجُلٌ شَدِيدُ بَيَاضِ الثِّيَابِ، شَدِيدُ سَوَادِ الشَّعْرِ، لَا يُرَى عَلَيْهِ أَثَرُ السَّفَرِ، وَلَا يَعْرِفُهُ مِنَّا أَحَدٌ. حَتَّى جَلَسَ إلَى النَّبِيِّ صلى الله عليه و سلم . فَأَسْنَدَ رُكْبَتَيْهِ إلَى رُكْبَتَيْهِ، وَوَضَعَ كَفَّيْهِ عَلَى فَخِذَيْهِ،\\
    وَقَالَ: يَا مُحَمَّدُ أَخْبِرْنِي عَنْ الْإِسْلَامِ.\\
    . . .\\
    وَقَالَ: يَا مُحَمَّدُ أَخْبِرْنِي عَنْ الْإِسْلَامِ.\\
    قَالَ: أَنْ تُؤْمِنَ بِاَللَّهِ وَمَلَائِكَتِهِ وَكُتُبِهِ وَرُسُلِهِ وَالْيَوْمِ الْآخِرِ، وَتُؤْمِنَ بِالْقَدَرِ خَيْرِهِ وَشَرِّهِ.\\
    . . .\\
    [رَوَاهُ مُسْلِمٌ]
\end{RLtext}
It was narrated on the authority of Umar (may Allah be pleased with him), who said:
\textbf{While we were one day sitting with the Messenger of Allah (peace be upon him), there appeared before us a man dressed in extremely white clothes and with very black hair. No traces of journeying were visible on him, and none of us knew him. He sat down close by the Prophet (peace be upon him), rested his knee against his thighs, and said, "O Muhammad! Inform me about Isl\=am."\\
. . .\\
but he went on to say, "Inform me about Im\=an."\\
He (the Messenger of Allah) answered, "It is that you believe in Allah and His angels and His Books and His Messengers and in the Last Day, and in Qadar (fate), both in its good and in its evil aspects."\\
. . .\\
}
[Muslim]
\textvtt{

\textit{Sheikhul Is\=am Muhammad Bin Saleh Al Uthaimin} (may All\=ah have mercy on him) has compiled the belief of the \textit{Ahlus-sunnah wal jama'ah} \footnote{Here I have mentioned the summary of the compilation of Sheikhul Isl\=am Muhammad Bin Saleh Al Uthaimin from the book named,
\begin{center}
\begin{RLtext}
    عقيدة أهل السنة والجماعة
\end{RLtext}
`The belief of \textit{Ahlus-sunnah wal jama'ah}'.
\end{center}
}. He says--- 

\subsection*{Belief in All\=ah}
\textit{Tawh\=id} is of three ---\textit{Ar-rububiyyah, Al-uluhiyyah} and \textit{Al-asma' was-sif\=at}. If any of these three is neglected his belief is invalid.

\subsubsection*{Tawh\=id Ar-rububiyyah}
We believe in the \textit{rububiyyah} of All\=ah. It means He is the \textit{Rabb} (Owner), Creator, Provider, Protector, Sustainer, He who has control over all things. The idolators of \textit{Makkah} believed in the \textit{rububiyyah} of All\=ah. All\=ah tells about them,
}
\begin{center}
    \begin{RLtext}
        قُل لِّمَنِ ٱلْأَرْضُ وَمَن فِيهَآ إِن كُنتُمْ تَعْلَمُونَ 
    \end{RLtext}
    \textbf{Say, (O Muhammad), "To whom belongs the earth and whoever is in it, if you should know?"} [23:84]
    \begin{RLtext}
        سَيَقُولُونَ لِلَّهِۚ قُلْ أَفَلَا تَذَكَّرُونَ 
    \end{RLtext}
    \textbf{They will say, "To Allāh." Say, "Then will you not remember?"} [23:85]
    \begin{RLtext}
        قُلْ مَن رَّبُّ ٱلسَّمَٰوَٰتِ ٱلسَّبْعِ وَرَبُّ ٱلْعَرْشِ ٱلْعَظِيمِ 
    \end{RLtext}
    \textbf{Say, "Who is Lord of the seven heavens and Lord of the Great Throne?"} [23:86]
    \begin{RLtext}
        سَيَقُولُونَ لِلَّهِۚ قُلْ أَفَلَا تَتَّقُونَ 
    \end{RLtext}
    \textbf{They will say, "[They belong] to Allāh." Say, "Then will you not fear Him?"} [23:87]
    \begin{RLtext}
        قُلْ مَنۢ بِيَدِهِۦ مَلَكُوتُ كُلِّ شَىْءٍ وَهُوَ يُجِيرُ وَلَا يُجَارُ عَلَيْهِ إِن كُنتُمْ تَعْلَمُونَ  
    \end{RLtext}
    \textbf{Say, "In whose hand is the realm of all things - and He protects while none can protect against Him - if you should know?"} [23:88]
    \begin{RLtext}
        سَيَقُولُونَ لِلَّهِۚ قُلْ فَأَنَّىٰ تُسْحَرُونَ 
    \end{RLtext}
    \textbf{They will say, "[All belongs] to Allāh." Say, "Then how are you deluded?"} [23:89]
\end{center}
\textvtt{
They believed in all these about All\=ah, yet they are the people of hell/disbelieve.

\subsubsection*{Tawhid Al-uluhiyyah}
We believe in the \textit{uluhiyyah} of All\=ah. It means He is the only true deity, who has the right our all types of worship. All other deities are false except Him. 

\subsubsection*{Tawhid Asma' Was-sif\=at}
We believe in all the names and attributes of All\=ah that are mentioned in the Qur\=an and \textit{Sunnah}.

\subsubsection*{Oneness of All\=ah}
We believe in the oneness of All\=ah. It means All\=ah has no partners in His \textit{rububiyyah, uluhiyyah and asma' was-sif\=at}. All\=ah says in the Qur\=an,
}
\begin{center}
    \begin{RLtext}
        رَّبُّ ٱلسَّمَٰوَٰتِ وَٱلْأَرْضِ وَمَا بَيْنَهُمَا فَٱعْبُدْهُ وَٱصْطَبِرْ لِعِبَٰدَتِهِۦۚ هَلْ تَعْلَمُ لَهُۥ سَمِيًّا 
    \end{RLtext}
    \textbf{Lord of the heavens and the earth and whatever is between them - so worship Him and have patience for His worship. Do you know of any similarity to Him?} [19:65]
\end{center}
\textvtt{

\subsubsection*{The Knowledge, Kingdom and Power of All\=ah}
We believe that---
}
\begin{center}
    \begin{RLtext}
        ٱللَّهُ لَآ إِلَٰهَ إِلَّا هُوَ ٱلْحَىُّ ٱلْقَيُّومُۚ لَا تَأْخُذُهُۥ سِنَةٌ وَلَا نَوْمٌۚ لَّهُۥ مَا فِى ٱلسَّمَٰوَٰتِ وَمَا فِى ٱلْأَرْضِۗ مَن ذَا ٱلَّذِى يَشْفَعُ عِندَهُۥٓ إِلَّا بِإِذْنِهِۦۚ يَعْلَمُ مَا بَيْنَ أَيْدِيهِمْ وَمَا خَلْفَهُمْۖ وَلَا يُحِيطُونَ بِشَىْءٍ مِّنْ عِلْمِهِۦٓ إِلَّا بِمَا شَآءَۚ وَسِعَ كُرْسِيُّهُ ٱلسَّمَٰوَٰتِ وَٱلْأَرْضَۖ وَلَا يَـُٔودُهُۥ حِفْظُهُمَاۚ وَهُوَ ٱلْعَلِىُّ ٱلْعَظِيمُ 
    \end{RLtext}
\end{center}
\textbf{
    Allāh - there is no deity except Him, the Ever-Living, the Self-Sustaining. Neither drowsiness overtakes Him nor sleep. To Him belongs whatever is in the heavens and whatever is on the earth. Who is it that can intercede with Him except by His permission? He knows what is [presently] before them and what will be after them, and they encompass not a thing of His knowledge except for what He wills. His Kursī extends over the heavens and the earth, and their preservation tires Him not. And He is the Most High, the Most Great.} [2:255]

\textvtt{
We believe that---
}
\begin{center}
    \begin{RLtext}
        هُوَ ٱللَّهُ ٱلَّذِى لَآ إِلَٰهَ إِلَّا هُوَۖ عَٰلِمُ ٱلْغَيْبِ وَٱلشَّهَٰدَةِۖ هُوَ    ٱلرَّحْمَٰنُ ٱلرَّحِيمُ \\
        هُوَ ٱللَّهُ ٱلَّذِى لَآ إِلَٰهَ إِلَّا هُوَ ٱلْمَلِكُ ٱلْقُدُّوسُ ٱلسَّلَٰمُ ٱلْمُؤْمِنُ    ٱلْمُهَيْمِنُ ٱلْعَزِيزُ ٱلْجَبَّارُ ٱلْمُتَكَبِّرُۚ سُبْحَٰنَ ٱللَّهِ عَمَّا يُشْرِكُونَ \\
        هُوَ ٱللَّهُ ٱلْخَٰلِقُ ٱلْبَارِئُ ٱلْمُصَوِّرُۖ لَهُ ٱلْأَسْمَآءُ ٱلْحُسْنَىٰۚ يُسَبِّحُ لَهُۥ مَا فِى ٱلسَّمَٰوَٰتِ وَٱلْأَرْضِۖ وَهُوَ ٱلْعَزِيزُ ٱلْحَكِيمُ 
    \end{RLtext}
\end{center}
\textbf{He is Allāh, other than whom there is no deity, Knower of the unseen and the witnessed. He is the Entirely Merciful, the Especially Merciful. He is Allāh, other than whom there is no deity, the Sovereign, the Pure, the Perfection, the Grantor of Security, the Overseer, the Exalted in Might, the Compeller, the Superior. Exalted is Allāh above whatever they associate with Him. He is Allāh, the Creator, the Producer, the Fashioner; to Him belong the best names. Whatever is in the heavens and earth is exalting Him. And He is the Exalted in Might, the Wise.} [59:22-24]

\textvtt{
We believe that---
}
\begin{center}
    \begin{RLtext}
        لِّلَّهِ مُلْكُ ٱلسَّمَٰوَٰتِ وَٱلْأَرْضِۚ يَخْلُقُ مَا يَشَآءُۚ يَهَبُ لِمَن يَشَآءُ إِنَٰثًا وَيَهَبُ لِمَن يَشَآءُ ٱلذُّكُورَ \\
        أَوْ يُزَوِّجُهُمْ ذُكْرَانًا وَإِنَٰثًاۖ وَيَجْعَلُ مَن يَشَآءُ عَقِيمًاۚ إِنَّهُۥ عَلِيمٌ قَدِيرٌ 
    \end{RLtext}
\end{center}
\textbf{To Allāh belongs the dominion of the heavens and the earth; He creates what He wills. He gives to whom He wills female [children], and He gives to whom He wills males. Or He makes them [both] males and females, and He renders whom He wills barren. Indeed, He is Knowing and Competent.} [42:49-50]

\textvtt{
We believe that---
}
\begin{center}
    \begin{RLtext}
        لَيْسَ كَمِثْلِهِۦ شَىْءٌۖ وَهُوَ ٱلسَّمِيعُ ٱلْبَصِيرُ 
    \end{RLtext}
    \textbf{There is nothing like unto Him, and He is the Hearing, the Seeing.} [42:11]
\end{center}

\textvtt{
\subsubsection*{All\=ah is the Knower of the unseen}
We believe that---
}
\begin{center}
    \begin{RLtext}
        إِنَّ ٱللَّهَ عِندَهُۥ عِلْمُ ٱلسَّاعَةِ وَيُنَزِّلُ ٱلْغَيْثَ وَيَعْلَمُ مَا فِى ٱلْأَرْحَامِۖ وَمَا تَدْرِى نَفْسٌ مَّاذَا تَكْسِبُ غَدًاۖ وَمَا تَدْرِى نَفْسٌۢ بِأَىِّ أَرْضٍ تَمُوتُۚ إِنَّ ٱللَّهَ عَلِيمٌ خَبِيرٌۢ 
    \end{RLtext}
\end{center}
\textbf{Indeed, Allāh [alone] has knowledge of the Hour and sends down the rain and knows what is in the wombs. And no soul perceives what it will earn tomorrow, and no soul perceives in what land it will die. Indeed, Allāh is Knowing and Aware.} [31:34]

\textvtt{
\subsubsection*{All\=ah Speaks}
We believe that--- All\=ah speaks what He wants, when He wants and how He wants.
}
\begin{center}
    \begin{RLtext}
        وَكَلَّمَ ٱللَّهُ مُوسَىٰ تَكْلِيمًا 
    \end{RLtext}
    \textbf{And Allāh spoke to Moses with [direct] speech.} [4:164]
    \vspace{10px}
    \begin{RLtext}
        وَلَوْ أَنَّمَا فِى ٱلْأَرْضِ مِن شَجَرَةٍ أَقْلَٰمٌ وَٱلْبَحْرُ يَمُدُّهُۥ مِنۢ بَعْدِهِۦ سَبْعَةُ أَبْحُرٍ مَّا نَفِدَتْ كَلِمَٰتُ ٱللَّهِۗ إِنَّ ٱللَّهَ عَزِيزٌ حَكِيمٌ 
    \end{RLtext}
\end{center}
\textbf{And if whatever trees upon the earth were pens and the sea [was ink], replenished thereafter by seven [more] seas, the words of Allāh would not be exhausted. Indeed, Allāh is Exalted in Might and Wise.} [31:27]

\textvtt{We believe that--- the words of All\=ah are complete and true from the view of information, just from the view of rules \& regulations and completely beautiful from the view of eloquence. All\=ah says,
}
\begin{center}
    \begin{RLtext}
        وَتَمَّتْ كَلِمَتُ رَبِّكَ صِدْقًا وَعَدْلًاۚ 
    \end{RLtext}
    \textbf{And the word of your Lord has been fulfilled in truth and in justice.} [6:115]
\end{center}

\subsubsection*{Qur'\=an is the Word of All\=ah}
\textvtt{
We believe that--- Qur'\=an is the Word of All\=ah. Truly He spoke it to Jibril and Jibril may the peace of All\=ah be upon him brought it (by the permission of All\=ah) to the heart of Prophet Muhammad may the peace and blessings of All\=ah be on him. All\=ah says,
}
\begin{center}
    \begin{RLtext}
        وَإِنَّهُۥ لَتَنزِيلُ رَبِّ ٱلْعَٰلَمِينَ \\
        نَزَلَ بِهِ ٱلرُّوحُ ٱلْأَمِينُ \\
        عَلَىٰ قَلْبِكَ لِتَكُونَ مِنَ ٱلْمُنذِرِينَ \\
        بِلِسَانٍ عَرَبِىٍّ مُّبِينٍ 
    \end{RLtext}
\end{center}
\textbf{And indeed, it [i.e., the Qur’\=an] is the revelation of the Lord of the worlds. The Trustworthy Spirit [i.e., Gabriel] has brought it down. Upon your heart, [O Muhammad] - that you may be of the warners. In a clear Arabic language.} [26:192-195]

\textvtt{
\subsubsection*{All\=ah is Over Everything}
We believe that--- All\=ah is above all the creation by His own self and attributes. Like All\=ah says,
}
\begin{center}
    \begin{RLtext}
        وَهُوَ ٱلْعَلِىُّ ٱلْعَظِيمُ
    \end{RLtext}
    \textbf{And He is the Most High, the Most Great.} [2:255]
\end{center}

\textvtt{
\subsubsection*{All\=ah Rose over His Throne}
We believe that---
}
\begin{center}
    \begin{RLtext}
        إِنَّ رَبَّكُمُ ٱللَّهُ ٱلَّذِى خَلَقَ ٱلسَّمَٰوَٰتِ وَٱلْأَرْضَ فِى سِتَّةِ أَيَّامٍ ثُمَّ ٱسْتَوَىٰ عَلَى ٱلْعَرْشِۖ 

    \end{RLtext}
\end{center}
\textbf{Indeed, your Lord is Allāh, who created the heavens and the earth in six days [Every day is like a thousand years of what we reckon.] and then rose over (Istawa) the Throne. [The Throne is the greatest of the creatures and is like a ceiling for them.]} [10:3]

\textvtt{
We believe it without questioning how and why.

\subsubsection*{All\=ah is with His Creation}
We believe that All\=ah is with His Creation. But it doesn't mean He is with them by Himself, indeed He is on His throne. From His throne, He knows all about His creation. He listens and watches everything. Gives kingdom to whom he wants and takes away kingdom from whom He wants. He is able and capable over all things from His throne. We don't say like the \textit{'Hululiyyah (Jahmiyyah)} that, All\=ah is with his creation on the same earth/place. 
}
\begin{center}
    \begin{RLtext}
        لَيْسَ كَمِثْلِهِۦ شَىْءٌۖ وَهُوَ ٱلسَّمِيعُ ٱلْبَصِيرُ \\
    \end{RLtext}
    \textbf{There is nothing like unto Him, and He is the Hearing, the Seeing.} [42:11]
\end{center}

\textvtt{
\subsubsection*{All\=ah Descends down to Our Sky}
The Messenger of All\=ah informed that--- In the last third of every night, All\=ah descends to our sky and says, 
}
\begin{center}
    \begin{RLtext}
        من يدعونى فأستجيب له من يسألنى فأعطيه من يستغفرنى فأغفر له
    \end{RLtext}
    \textbf{Who will call me? I will answer his call. Who will ask me? I will give. Who will ask forgiveness to me? I will forgive.}\footnote{Muatta' 1/214, Bukh\=ari 9/25,26, Muslim 1/521}
\end{center}

\textvtt{
\subsubsection*{All\=ah Does What He Wills}
% ًWe believe that---
We believe that---
}
\begin{center}
    \begin{RLtext}
        فَعَّالٌ لِّمَا يُرِيدُ 
    \end{RLtext}
    \textbf{[All\=ah surely] Effecter of what He intends.} [85:16]
\end{center}

\textvtt{
\subsubsection*{All\=ah's Will is of Two Types}
We believe that--- All\=ah's will is of two types: 1. \textit{Kauniyyah} 2. \textit{Shar'iyyah}
}
\begin{enumerate}
    \textvtt{
    \item \textit{Kauniyyah}: By this type of will of All\=ah, the task is completed. But is not necessary that All\=ah would like that. Like All\=ah says,}
    \begin{center}
        \begin{RLtext}
             وَلَوْ شَآءَ ٱللَّهُ مَا ٱقْتَتَلُوا۟ وَلَٰكِنَّ ٱللَّهَ يَفْعَلُ مَا يُرِيدُ 
        \end{RLtext}
        \textbf{And if Allāh had willed, they would not have fought each other, but Allāh does what He intends.} [2:253]
    \end{center}
    \textvtt{
    \item \textit{Shar'iyyah}: By this type of will, the task doesn't need to be fulfilled which All\=ah wills. But in this case, the matter has to be liked by All\=ah.}
    \begin{center}
        \begin{RLtext}
            وَٱللَّهُ يُرِيدُ أَن يَتُوبَ عَلَيْكُمْ    
        \end{RLtext}
        \textbf{All\=ah wants to accept your repentance.} [4:27]
    \end{center}
\end{enumerate}
\textvtt{
We believe that--- both wills of All\=ah are within His \textit{'Hikmah} (wisdom). In this matter, we may or may not understand some of His wisdom. It doesn't matter, whether our intellect realizes it or not. In all conditions, All\=ah is the greatest \textit{'H\=akim}.
}
\begin{center}
    \begin{RLtext}
        أَلَيْسَ ٱللَّهُ بِأَحْكَمِ ٱلْحَٰكِمِينَ 
    \end{RLtext}
    \textbf{Is not Allāh the most just of judges?} [95:8]
\end{center}

\textvtt{
\subsubsection*{All\=ah's Love}
We believe that--- All\=ah loves His friends.
}

