\chapter{Introduction}
\textvtt{
Great vision, which was once our property, now it seems that it no longer exists in us. There was a time when a Muslim would wake up confident, fearless, thanking his Lord All Mighty\footnote{The sunnah is, when you wake up from bed in the morning, our prophet taught us to recite,
\begin{center}
    \begin{RLtext}
    اَلْحَمْدُ لِلّٰهِ الَّذِيْ أَحْيَانَا بَعْدَ مَا أَمَاتَنَا، وَإِلَيْهِ النُّشُوْرُ
    \end{RLtext}
    “All praise is for Allaah who gave us life after having taken it from us and unto Him is the resurrection” [Al-Bukhari]
\end{center}
This dua indicates the dependence and thankfulness of a Muslim to his Rabb. When you know your Rabb, you can not but thank Him every single moment. This boosts an individual and he feels free from every burden of his life. Look at the wording of the dua, I thank you yaa Rabb, for keeping me alive and giving me another opportunity to live, to breathe. This feeling will push you to work hard on that day.
}. Now it seems everyone is in fear, even a child wakes up in fear. People fear of losing everything. So, they go and take so many insurances, thinking and hoping that these would save them.

If you go to the Western world, you will find there are PhD degrees in vision. It seems that once what was ours, now others are learning it and benefiting from it. I will try to give a glimpse of how our predecessors were, how they used to think, and things like that.

Allaah testifies that we(Muslims) are the best nation. But how can we be the best without true vision?
}
