\chapter{Islam Changed the Visions of the Bedouins}\label{islamAndBeduins}
\textvtt{
Can you imagine what life was like before Islam in Arabia? If you read the chronicles, no historian ever called them a civilization. They were very simple people, nothing was organized in their society. All they used to do was, first they tried to earn, then they used to spend that money on drinking, singing, and women. Mainly they spent on all entertainment-based things. No high ambition in life. Passing the days waiting to die someday, hoping it won’t happen. 

Allaah rabbul ‘izaah sent Islam, and through this, Allaah gave them purpose. So every moment of their life became about achieving the purpose, which is the ridaa (please) of the Lord and His Jannah. You would find them waking in the middle of the night and standing in long sessions of salat [prayer]. Very productive. Why? “Because I’m trying to earn the pleasure of Allaah”. And don’t think that they used to sleep all day the next day. 

A beautiful case with Abu Bakr As-Siddiq (may Allaah be pleased with him). Abu Hurairah (may Allaah be pleased with him) Narrates that the Prophet (peace and blessings be upon his soul) came to the sahaba one day and asked, “Who amidst you woke up today fasting?” So Abu Bakr (may Allaah be pleased with him) said, “I’m fasting, O Prophet of Allaah.” He (peace and blessings be upon his soul)  said, “Who has gone to a funeral procession today?” [i.e. who has helped a funeral procession with the digging, carrying, burying, etc?] He(Abu Bakr) said, “I have, O Prophet of Allaah.” He (peace and blessings be upon his soul) asked, “Which one amidst you have gone, found a poor person and given him food?” Abu Bakr said, “I have, O Prophet.” And then Rasool said, “Who has visited a sick person today?” Abu Bakr said, “I have.” And the scholars said that this was by the time of duha [Morning]. Can you imagine! It was still morning and he had already done all these things. Can you tell yourself, why is he (Abu Bakr) doing these? To please Allaah, and through that, gain Jannah.  

In the pre-ignorant days before Islam, One man came to young ‘Umar Ibnul Khattab and asked him, “O ‘Umar! What is the purpose/mission of your life?” ‘Umar Replied\footnote{‘Umar (may Allaah be pleased with him) was not a Muslim yet, at that time.
}, “I want to have a herd of sheep so that it can produce enough milk and provision for my family”. After ‘Umar (may Allaah be pleased with him) became the ‘Amirul Mu’minin(the leader of the believers) the same man came to him and asked the same question, “O ‘Umar! What is your purpose in life now?\footnote{He meant, oh ‘Umar (may Allaah be pleased with him), Islam came and changed you, we see all your changes after Islam, but that’s all external, what's your inside now? Do you still possess the same dreams of the days of ignorance, or has Islam changed your vision too?} ‘Umar (may Allaah be pleased with him) replied, 
\begin{center}
    \textit{
        “I want the Deen of Allaah to prevail all over the globe”. }
\end{center}
\par Beautiful story with ‘Uthman Ibn ‘Affan (may Allaah be pleased with him)  ---A man came to meet him, but he found him in salat [prayer], he completed the whole Qur’an and finished the night in prayer, the man waited the whole night; when his two units of salat would complete and he would talk? And even in his seventies, he used to buy slaves and at night he used to pray and the slave would hold the parchment of the Qur'an in front of him the whole night. He used to complete the whole Qur'an by night and in the morning he would free that slave. 
}