\chapter{The vision of our Beloved Messenger}
\textvtt{
One day our Messenger (peace and blessings be upon his soul) was praying in front of the kaaba\footnote{This was at the time of \textit{Makkah}, when Muslims were vulnerable, being oppressed, and not even given freedom to worship their Maker Alone.
}. Abu Jahal (Abul Hakam Ibn Hisham) came up with a basket of dung and intestines of a dead camel, poured it on the blessed body of our beloved, and started swearing at our Prophet. He (peace and blessings be upon his soul) kept praying. Someone went and told His daughter Fatima may Allah be pleased with her, -they have poured dirt on your Father. She came crying (a young little girl at that stage), started cleaning the dirt, and crying and cursing them. But the Prophet peace and blessings be upon his soul said,
\begin{center}
    \textit{“Don't worry O Fatima! What your Father has brought, will enter every home on the planet.”}
\end{center}
See the vision! At what time? With which resources? With which military power? Nothing. At a time when He (peace and blessings be upon his soul) could not protect his Muslim brothers and even himself. But his vision was, “This Deen will prevail in every house of this globe.”

And when He (peace and blessings be upon his soul) was in \textit{Makkah}, you know how the situation was in the early days of \textit{Makkah}. This was then when Umar Ibnul Khattab and Hamza Ibnu Abdil Muttalib (may Allaah be pleased with them both) didn’t accept Islam yet\footnote{Islam was strengthened by their acceptance of Islam.}. Then He (peace and blessings be upon his soul) used to say to His companions (may Allaah be pleased with them),
\begin{center}
    \textit{“Do not be disheartened by your lack of strength or small number, or by the power enjoyed by the Quraysh masters and their arrogance. By Allaah, other than Whom there is no deity, what Allaah has promised shall come true. This deen shall reach the furthest points in the east and west. And Allaah will give us the kingdom of Persia and Byzantium\footnote{At the time of Prophet peace be upon Him, there were two main superpowers. On one side there was the Roman Empire and on the other side, there was the Persian Empire. These two empires reached the zenith of power. The Arab peninsula was somewhere sandwiched between these two empires. It's beyond imagination how powerful they were against these Arabs.
    }”.}
\end{center}
I imagine it this way, if today a man from a rural area of Bangladesh would say to his people, ``Follow me and pretty soon you will overcome the superpowers of today's time.''  How would the people of that village behave with that man? 

He (peace and blessings be upon his soul) also told them, 
\begin{center}
    \textit{“If you today suffer hardship on account of your faith, remember the future Allaah has promised. You will then find your present hardship easier to bear.”
    }
\end{center}
\par Remember the \textit{hijrah}. Keep in mind what the Rasul bore in \textit{Makkah}, why He (peace and blessings be upon his soul)  had to migrate to \textit{Madina}. And even the \textit{Quraysh} hatched a plot to kill the Prophet. You know the story. Then the permission from Allaah came to migrate. On that night when 100 warriors of \textit{Makkah} came to kill the Rasul, He (peace and blessings be upon his soul) managed to go out from the city of \textit{Makkah} miraculously with his friend Abu Bakr as-Siddiq (may Allaah be pleased with him). They started the journey at night and when they climbed down from the cave (Ghar-e-Thawr)\footnote{Prophet (peace and blessings be upon his soul) wanted to misguide the soldiers by going south of \textit{Makkah} initially. So that the enemies would assume that Rasul is going somewhere south. He (peace and blessings be upon his soul) and Abu Bakr (may Allaah be pleased with him) went and hid themselves in Ghar-e-Thawr. The enemies followed them by their footsteps and unfortunately reached that mountain and climbed it. But Allaah miraculously saved His Messenger (peace and blessings be upon his soul). Allaah Almighty says about that incident,
\begin{center}
\begin{RLtext}
    	إِلَّا تَنصُرُوهُ فَقَدْ نَصَرَهُ ٱللَّهُ إِذْ أَخْرَجَهُ ٱلَّذِينَ كَفَرُوا۟ ثَانِىَ ٱثْنَيْنِ إِذْ هُمَا فِى ٱلْغَارِ إِذْ يَقُولُ لِصَـٰحِبِهِۦ لَا تَحْزَنْ إِنَّ ٱللَّهَ مَعَنَا ۖ فَأَنزَلَ ٱللَّهُ سَكِينَتَهُۥ عَلَيْهِ وَأَيَّدَهُۥ بِجُنُودٍۢ لَّمْ تَرَوْهَا وَجَعَلَ كَلِمَةَ ٱلَّذِينَ كَفَرُوا۟ ٱلسُّفْلَىٰ ۗ وَكَلِمَةُ ٱللَّهِ هِىَ ٱلْعُلْيَا ۗ وَٱللَّهُ عَزِيزٌ حَكِيمٌ 
\end{RLtext}    
\end{center}
\textbf{If you do not aid him [i.e., the Prophet (peace and blessings be upon his soul)] - Allaah has already aided him when those who disbelieved had driven him out [of \textit{Makkah}] as one of two, when they were in the cave and he [i.e., Muhammad (peace and blessings be upon his soul)] said to his companion, "Do not grieve; indeed Allaah is with us." And Allaah sent down His tranquility upon him and supported him with soldiers [i.e., angels] you did not see and made the word of those who disbelieved the lowest, while the word of Allaah - that is the highest. And Allaah is Exalted in Might and Wise.}[9:40]
}  and finally started heading towards \textit{Madina}. News has been spread far away amongst the arab tribes that whoever catches or kills Muhammad and His companion, will be rewarded with 100 camels for each. Amidst the Bedouins there was a man named Suraqa Ibn Maalik, this man Suraqa rushed towards that direction with his horse and weapon\footnote{ As Suraqa was a Bedouin, he knew the desert better. So somehow he managed to track our Beloved and Abu Bakr with.}. Unfortunately, Suraqa Ibn Maalik finds them and from a distance, he takes his weapon out and runs. And Abi Bakr sees him galloping towards them. He said, “Yaa Rasulallah! Look!.” He (peace and blessings be upon his soul) turns and makes dua, “Yaa Rabb! Suffice me from his evil, any way You choose.” So Allaah rabbul 'izzah dug the lift legs of the horse into the ground, and Suraqa fell off the horse. And in one of the narrations, Suraqa got up and said, “Yaa Muhammad, I come with no harm, pray to your Lord to release me from this ”. Then a while later, Suraqa got up, and out of his greed, he came back again to attack them. Prophet (peace and blessings be upon his soul) looks at him and prays again the same du’a. This time the horse went deeper and the same thing repeated. So this time Suraqa understood that ``The man is out of bounds, I’m not supposed to touch Him.'' Now a funny thing happens. The same man who came to kill our Beloved now comes to Him and says, “Please, give me a certificate that I am safe”. Like he says, promise me safety. So the Prophet ‘alaihis salatu wassalam tells, ‘Amr Ibn Fuhairah may Allaah be pleased with him, “‘Amr! Write for him ---From Muhammad, the Messenger of Allaah, Suraqa Ibnu Maalik is guaranteed safety from Allaah and His Messenger ”. Now Suraqa says, “I came for the 200 camels. Now that has gone, please write some financial things as well ”. Then the Rasul (peace and blessings be upon his soul) said, 
\begin{center}
    \textit{“I promise you the wristbands of Kisra ”.}
\end{center}
Suraqa said, “The Empire!!?” He (peace and blessings be upon his soul) said, “Yes the empire”. Suraqa says, “Write it”. So ‘Amr wrote it and gave it to Suraqa. Suraqa went.

Rasul (peace and blessings be upon his soul) reached \textit{Madina}, Islam was established, and Rasul (peace and blessings be upon his soul) passed away. Then once Suraqa goes to the successor of our Prophet, Abu Bakr as-siddiq (may Allaah be pleased with him) with that parchment, “Your Prophet gave me this promissory note”. But Abu Bakr (may Allaah be pleased with him) couldn’t give him that then what our beloved promised Suraqa. Then Abu Bakr (may Allaah be pleased with him) passed away. At his death, he gave that parchment to ‘Umar (may Allaah be pleased with him) that Suraqa had been promised. And in the time of 'Umar Ibnul Khattab (may Allaah be pleased with him) the land of Kisra (Persian Empire) was conquered. And all the treasures were sent to \textit{Madina}. These treasures were opened. And the wristbands of the kings of Persians were also brought. When ‘Umar said, “What is this?” They said, “These are the wristbands of Kisra ”. He said, “Go and call Suraqa Ibnu Maalik ''. So they called Suraqa, and Suraqa is an old man now. ‘Amirul Mu’minin ‘Umar (may Allaah be pleased with him) said,
\begin{center}
    \textit{“Here! Wear these. And testify that the Messenger of Allaah spoke the truth”.}
\end{center}
So Suraqa picked it up crying and sobbing, “Sadaqa Rasulallah, Sadaqa Rasulallah, (The Messenger has spoken the truth, The Messenger has spoken the truth)”. 

Remember the battle of the trench[khandaq]\footnote{After the migration of \textit{Madina}, the first battle was Badr. In it, Muslims were victorious miraculously. Allaah helped them with a thousand Angels. Then Quraish wanted to take revenge for what happened at Badr and prepared for the battle of Uhud. At Uhud, some mistakes happened and Muslims learned some lessons. Then Quraish again hatched a plan with some Jews of \textit{Madina} and attacked, and this time they attacked directly to the city of \textit{Madina}. So to save the city, with the plan of Salman Al Farsi (may Allaah be pleased with him) Prophet (peace and blessings be upon his soul) decided to dig a trench at the vulnerable sides of the city of \textit{Madina}. 
}, when the Sahaba(companions) were digging the long trench at the outskirts of \textit{Madina},\\
It was narrated from Abu Sukainah, a man from among the Muhajirin, that a man among the Companions of the Prophet (peace and blessings of Allaah be upon his soul) said:
}
\textbf{"When the Prophet (peace and blessings be upon his soul) commanded them to dig the trench (Al-Khandaq), there was a rock in their way preventing them from digging. The Messenger of Allah (peace and blessings be upon his soul) stood, picked up a pickaxe, put his Rida' (upper garment) at the edge of the ditch, and said: `And the Word of your Lord has been fulfilled in truth and in justice. None can change His Words. And He is the All-Hearer, the All-Knower.' One-third of the rock broke off while Salman Al-Farisi\footnote{Salman al Farisi (may Allaah be pleased with him), he was from Isfahan, Persia. Miraculously, he was brought to \textit{Madina} by Allaah rabbul 'izzah. He entered into the fold of Islam, served, and practiced the deen of Allaah. When the battle of the trench came, everyone was worried about how to protect the city and its people. Then Salman al Farisi (may Allaah be pleased with him) gave this idea, he said, “Yaa Rasulallah, in Persia, whenever an enemy came to attack us, we used to dig a trench about 16x10 feet around the city. The Messenger of Allaah (peace and blessings be upon his soul) accepted his idea, so Salman al Farsi became the hero of the battle of Khandaq (trench).} was standing there watching, and there was a flash of light when the Messenger of Allah (peace and blessings be upon his soul)struck (the rock). Then he struck it again and said: 'And the Word of your Lord has been fulfilled in truth and in justice. None can change His Words. Ans He is the All-Hearer, the All-Knower' And another third of the rock broke off and there was another flash of light, which Salman saw. Then he struck (the rock) a third time and said: 'And the Word of your Lord has been fulfilled in truth and in justice. None can change His Words. And He is the All-Hearer, the All-Knower.' The last third fell, and the Messenger of Allah (peace and blessings be upon his soul) came out, picked up his Rida' and sat down. Salman said: `O Messenger of Allah, Each time you struck the rock there was a flash of light.' The Messenger of Allah (peace and blessings be upon his soul) said to him: 'O Salman, did you see that?' He said: 'Yes, by the One Who sent you with the truth, O Messenger of Allah.' He said: 'When I struck the first blow, the cities of Kisra and their environs were shown to me, and many other cities, and I saw them with my own eyes.' Those of his Companions who were present said: 'O Messenger of Allah, pray to Allah to grant us victory and to give us their land as spoils of war, and to destroy their lands at our hands.' So the Messenger of Allah (peace and blessings be upon his soul) prayed for that. (Then he said:) 'Then I struck the second blow and the cities of Caesar and their environs were shown to me, and I saw them with my own eyes.' They said: 'O Messenger of Allah, pray to Allah to grant us victory and to give us their lands as spoils of war, and to destroy their lands at our hands.' So the Messenger of Allah (peace and blessings be upon his soul) prayed for that. (Then he said:) 'Then I struck the third blow and the cities of Ethiopia were shown to me, and the villages around them, and I saw them with my own eyes.' But the Messenger of Allah (peace and blessings be upon his soul) said at that point: 'Leave the Ethiopians alone so long as they leave you alone, and leave the Turks alone so long as they leave you alone.'"} \footnote{Hadith Hasan,\\
Sunan an-Nasa'i, Book 25, Hadith 92}

\textvtt{
\par By this word of the Messenger peace be upon Him, the companions understood that if they truly believe and sincerely obey Allaah’s Messenger, what they’re facing today won’t trouble them much. Since they now know certainly what Allaah will give them in the future. If they(Muslims) are going to parish now by these mushriks of Quraish who, then how this deen would prevail on the globe! No one at that spot didn't even think that, let us first tackle the Quraish in this battle, then we would discuss about Romans and Persians. Because their vision was solid, that this calamity won't be able to harm them much (although the army of the Quraish was stronger than them at that time), they would conquer the world for sure. 
}