\chapter{The Miraculous Rise of Islam}

\textvtt{
If you look into history, whenever a nation arrived above others, certain things are prerequisites. For example, water; water is a primary requirement for a civilization to grow. Yet Makkah had no water. Even today one-third of the Arabia is considered as vacant land. Also requires an educated and united mass, trained and disciplined huge military, political stability, etc. But that didn’t exist in Makkah or Arabia. Before Islam, only a few people could read and write. Compared to contemporary civilizations they didn’t have military capability and political stability. They didn’t have any treasures like gold or silver. Even they didn’t have enough food for themselves, because the land was unvegetated. And there is a Hadeeth about the Prophet (peace and blessings be upon his soul), He was in an orchard, picking dates from the floor and ate. So, food was rare and limited.

Yet, out of nowhere the civilization not only survives, but within a short few decades, it catches up to the other civilizations. And not only catches up to them, it overtakes them. And not only overtakes them, it flourishes and excels.\\

I will just mention some points here. 

\section*{Allaah rabbul 'izzah sent to them His Messenger}
Allaah rabbul 'izzah intervened in their lives by a Prophet. Allaah rabbul 'izzah didn’t intervene with gold, and He could have intervened with gold. As for the Prophet Aiyyub (peace and blessings be upon his soul), he was ill for many years, and then Allaah cured him. And then one day he was bathing and gold nuggets started to fall from the sky for him and he collected them\footnote{Ibn Abi Hatim recorded from Abu Hurayrah that the Prophet said:
\begin{RLtext}
    لَمَّا عَافَى اللهُ أَيُّوبَ أَمْطَرَ عَلَيْهِ جَرَادًا مِنْ ذَهَبٍ فَجَعَلَ يَأْخُذُ مِنْهُ بِيَدِهِ وَيَجْعَلُهُ فِي ثَوْبِهِ قَالَ فَقِيلَ لَهُ يَا أَيُّوبُ أَمَا تَشْبَعُ قَالَ يَا رَبِّ وَمَنْنَيشْبَعُ مِنْ رَحْمَتِك
\end{RLtext}
When Allah healed Ayub, He sent upon him a shower of golden locusts, and he started to pick them up and gather them in his garment. It was said to him, "O Ayub, have you not had enough!"
}. So, had Allaah rabbul 'izzah wanted to equip them with gold, it would have rained from the sky. It’s easy for Allaah rabbul 'izzah, but Allaah didn’t.

For the children of Israel Allaah rabbul 'izzah opened water\footnote{Allaah says in the Qur'an, 

\begin{center}  
\begin{RLtext}  
    وَإِذِ ٱسْتَسْقَىٰ مُوسَىٰ لِقَوْمِهِۦ فَقُلْنَا ٱضْرِب بِّعَصَاكَ ٱلْحَجَرَۖ فَٱنفَجَرَتْ مِنْهُ ٱثْنَتَا عَشْرَةَ عَيْنًاۖ قَدْ عَلِمَ كُلُّ أُنَاسٍ مَّشْرَبَهُمْۖ كُلُوا۟ وَٱشْرَبُوا۟ مِن رِّزْقِ ٱللَّهِ وَلَا تَعْثَوْا۟ فِى 
    ٱلْأَرْضِ مُفْسِدِينَ
\end{RLtext}
\end{center}
\textbf{And [recall] when Moses prayed for water for his people, so We said, "Strike with your staff the stone." And there gushed forth from it twelve springs, and every people [i.e., tribe] knew its watering place. "Eat and drink from the provision of Allah, and do not commit abuse on the earth, spreading corruption."} [2:60]
}. Allaah could have done that, but Allaah rabbul 'izzah didn’t.

Allaah rabbul 'izzah could have brought food from heaven for them, that listen people! you need nourishment, here is your food and go do My duty. Allah didn’t. Yet Allaah did it for Banu Israel\footnote{Allaah says in the Qur'an
\begin{center}
    \begin{RLtext}
        وَقَطَّعْنَٰهُمُ ٱثْنَتَىْ عَشْرَةَ أَسْبَاطًا أُمَمًاۚ وَأَوْحَيْنَآ إِلَىٰ مُوسَىٰٓ إِذِ ٱسْتَسْقَىٰهُ قَوْمُهُۥٓ أَنِ ٱضْرِب بِّعَصَاكَ ٱلْحَجَرَۖ فَٱنۢبَجَسَتْ مِنْهُ ٱثْنَتَا عَشْرَةَ عَيْنًاۖ قَدْ عَلِمَ كُلُّ أُنَاسٍ مَّشْرَبَهُمْۚ وَظَلَّلْنَا عَلَيْهِمُ ٱلْغَمَٰمَ وَأَنزَلْنَا عَلَيْهِمُ ٱلْمَنَّ وَٱلسَّلْوَىٰۖ كُلُوا۟ مِن طَيِّبَٰتِ مَا رَزَقْنَٰكُمْۚ وَمَا ظَلَمُونَا وَلَٰكِن كَانُوٓا۟ أَنفُسَهُمْ يَظْلِمُونَ 
    \end{RLtext}
\end{center}
\textbf{And We divided them into twelve descendant tribes [as distinct] nations. And We inspired to Moses when his people implored him for water, "Strike with your staff the stone," and there gushed forth from it twelve springs. Every people [i.e., tribe] knew its watering place. And We shaded them with clouds and sent down upon them manna and quails, [saying], "Eat from the good things with which We have provided you." And they wronged Us not, but they were [only] wronging themselves.} [7:160]
}, manna and salwa came down from the heavens for them. 

The only thing Allaah rabbul 'izzah gave them, the intervention, was a prophet, a messenger. By definition, carrying a message. The message is the \textit{deen} of Islam. So Allaah rabbul 'izzah, through the \textit{deen} did the following-
\begin{enumerate}[label=\roman *.]
    \item Allaah rabbul 'izzah changed their hearts.
    \item Allaah rabbul 'izzah changed their minds.
    \item Allaah rabbul 'izzah changed their conduct.
\end{enumerate}
And the rest was organic. And once someone embodies the above changes that Allaah sent, he can’t help but become successful, in this life and the next.

\section*{Allaah rabbul 'izzah changed their hearts}
When the Rasul (peace and blessings be upon his soul) was summoned to the office of prophethood, he came to the people with this message,
\begin{center}
    \begin{RLtext}
        يا أيها الناس, قل لا إله إلا الله, تفلح
    \end{RLtext}
\end{center}
\textit{O people! Make the proclamation that there’s none worthy of worship save one mighty Allaah and success will be yours \footnote{Allaah says,
\begin{center}
    \begin{RLtext}
        قَدْ أَفْلَحَ ٱلْمُؤْمِنُونَ 
    \end{RLtext}
    \textbf{Successful indeed are the believers}[23:01]
\end{center}
}.}

This is a matter of the heart. In your heart of hearts, there should be nothing that you rely on, except the one Mighty Allaah. 

So the Rasul came at a time when there were 360 idols around the Ka’baa. To an Arab population, who were like ---easily offended, sensitive creatures, and deeply devout to these idols. As Khalid Ibnul Walid (may Allah be pleased with him) remembers- ``My father sacrificed 100 camels for a single idol.'' Proof that they had a lot of devotion to those idols. Yet, wrong belief. Can anyone imagine! Man bowing down to a stone, asking help from it.

Allaah rabbul 'izzah sent the messenger to correct the belief first. So the rasul came and declared- there is none worthy of worship except Allaah. It was a pretty courageous statement to make\footnote{When the Prophet (peace and blessings be upon his soul) called people for tawhid in a situation where there were 360 Idols around the Ka’ba, the people found it very strange. That’s why Allaah says, 
\begin{center}
    \begin{RLtext}
        أَجَعَلَ ٱلْـَٔالِهَةَ إِلَـٰهًۭا وَٰحِدًا ۖ إِنَّ هَـٰذَا لَشَىْءٌ عُجَابٌۭ
    \end{RLtext}
    \textbf{Has he reduced [all] the gods to One God? Indeed, this is something totally astonishing.} [38:5]
\end{center}
}. And in a time where there’s no police protection, it's a difficult time.

So, harassment started, abuse started, imprisonment started, torture started, assassination started. They (those that kind of accepted Islam) bore the brunt of it.

Within a few years those few that accepted the \textit{deen}, the superstitious hocus pocus of idols disappeared and a true belief of the one mighty God entered the hearts. And that did a few things.

The first one, it gave access to the normal human being to the majesty of the Creator. For years, they were turning to rocks that couldn’t do anything. Now they have access to Allaah, the Creator of the heavens and the earth. And that is a game changer. You know, at the time of ‘Umar Ibnul Khattab (may Allah be pleased with him) Muslims fought the Persians. One of the mighty generals of the Persians was caught and brought to the court of ‘Umar, tied up. ‘Umar (may Allah be pleased with him) looked at him- Yesterday you were on a throne, you had a crown, entourage, pomp and ceremony…. And now you’re tied up! What happened! You were all that. Then what the Persian general replied which every Muslim should have known. He said, 
\begin{center}
    \textit{“When the fight was against us and you, it was easy. But now how can I fight with the One in the heavens”.}
\end{center} 
This means that now Allaah is in the equation, we have no power against Him.

So these simple people now have access to their Creator and with that came all the treasures of the Creator. For example-

\subsection*{a. The first campaign, Badr}
Muslims were only 313 against a thousand strong. And there are narrations which mention, that there were only 8 sowards amidst the Muslims. They hadn’t come for a battle. They came to raid a caravan. So Allaah gives the cause of their success, because we know they were victorious, and uprooted the enemy out. Allah said, 
\begin{center}s
    \begin{RLtext}
        إِذْ تَسْتَغِيثُونَ رَبَّكُمْ فَٱسْتَجَابَ لَكُمْ أَنِّى مُمِدُّكُم بِأَلْفٍ مِّنَ ٱلْمَلَٰٓئِكَةِ مُرْدِفِينَ 
    \end{RLtext}
\end{center}
}
\textbf{(Remember) when you were asking help from your Lord, and He answered you, "Indeed, I will reinforce you with a thousand from the angels, following row after row."}[8:9]

\textvtt{
Allah sent them. And Rasul is on the battlefield, He (peace and blessings be upon his soul) says,
}
\textbf{Here’s Gibril, dressed for the war”.} \textvtt{And you would think that the Prophet is encouraging his companions. There were two people, standing on a mountain nearby (nonmuslims, bedouins), waiting for the battle to finish so that they could come down and collect what had fallen from the army and stuff like that. And suddenly one of them died. So after the war, they asked the other one, “Why did your friend die?" He said, “His heart burst”. They asked, “Why did his heart burst?” He said, “Out of fear.” They said, “What fear?” He said,
\begin{center}
    \textit{“We heard the neighing of the horses from the clouds above and saw the sparks of their hooves. So his heart burst and died.”}
\end{center}

Also inside the campaign of Badr, a Muslim chasing a kaafir, and before he reaches him the man is slain. And there are also other instances where a sahabi called a kaafir by name whom he knew from Makkah on the battlefield, “O so and so! Come, fight with me.” And the kaafir replied, “I’m not him.” My point is Angels were on the battlefield. What it (Imaan) did? It gave first and foremost, access to the One above the heavens. And if Allaah rabbul 'izzah is on your side everything else will be taken care of.

\subsection*{b. Imaan removed all types of fears from their hearts:}
All the success you want is on the other side of fear. And all the bad situations under which an individual is, because of fear. Fear is what holds people back. When there is no fear of Allaah in the heart, Allaah fills it with the fear of everything else.

The belief of the people of Makkah was based on superstitions, idols, and false deities. It was a life filled with fear. Imaan came and released them from it all. And they became what I call, superhumans. Because if you look at the \textit{sahaba}, the challenges they faced, the obstacles they conquered, a normal human can't do. Should I mention some examples?

\subsubsection*{Battle of Mu'ta}
Confrontation is something that all fear. War is a scary concept. When two equals are fighting, it is scary. The odds that the companions faced, we can't even imagine. The Prophet (peace and blessings be upon his soul) sent around three thousand to Mu'ta. Although the scholars differed, one narration says, a hundred and fifty thousand came against them. And the Muslims were expecting the arab tribes to come to the battle but there came instead of the actual Roman soldiers. The Prophet (peace and blessings be upon his soul) sent them with the instructions that, 
\begin{center}
    \textit{Zayed Ibn Haarithah (may Allaah be pleased with him) is in charge. If Zaid falls, Ja'far Ibn Abi Talib (may Allaah be pleased with him) will be your leader, if Za'far falls, then Abdullah Ibn Rawaha (may Allaah be pleased with him) will take the rains and if he falls then choose a leader from yourselves.}
\end{center}
Can you imagine yourself in that situation! but they were facing unimaginable odds. And you would think that they would panic, shake, anxious, worried! you won't find it in them. It is as though they didn't know fear existed.

This is the second commander, Ja'far Ibn Abi Talib, so the first one Zayed fell already. Ja'far holds the standard and gallops into the enemy. And then he thinks, ``In difficulty, the horse might run back'', so jumps off the horse and this is heard on the battlefield him saying,
\begin{center}
\begin{RLtext}
    يا حبذا الجنة واقترابها طيبة وباردة شرابها والروم روم قد دنا عذابها كافرة بعيدة أنسابها.
\end{RLtext} 
\textit{O the beauty and delight of Jannah and how close you are! How pleasant and cool is its drink! The Romans are a Roman whose torment is approaching, as an infidel whose lineage is distant!}
\end{center} 
On the battlefield, he should be scared against the Romans, but it seems that just beyond this he is in Jannah. Do you see what Imaan does? It made the obstacles of this life nothing. And he is not the isolated one. Abdullah Ibn Umar (may Allaah be pleased with him) said:
}
\textbf{
``I was present amongst them in that battle and we searched for Ja'far bin Abi Talib and found his body amongst the bodies of the martyred ones, and found over ninety wounds over his body, caused by stabs or shots (of arrows).''}
\textvtt{
They struck him, his right hand got cut, so he held the flag with his left hand. They cut off his left hand, he held the flag with his chest, then they stabbed him.

Then when the standard came to the third commander 'Abdullah Ibn Rawaha (may Allaah be pleased with him), his cousin gave him a piece of meat to eat. For a second he tarried and said this to himself, 
\begin{center}
    \textit{O soul! Why are you afraid of death?\\ This is what you were seeking.\\ You know what your desire is, just in front of you.}
\end{center}
Difficulties like that, where we would think that they would break, but it did not affect them. Why? because of the power of Imaan. Imaan gave them the strength to overcome all types of odds. This is just fear,

\subsubsection*{Accute Hunger came}
The Prophet (peace and blessings be upon his soul) is in the battle of Khandaq(trench). They were digging the trench, working. Hunger reached a level that they started tying rocks on their bellies (today we call it gastric bypass). So that, their stomach gets shrunk and they don't feel hungry. They were still working. If anyone working with a rock on his stomach, the morale gets pretty low. But these people started to compare the size of the rocks, "Who's got the biggest rock!!" And when they reached to Prophet (peace and blessings be upon his soul), they found three rocks on his blessed stomach, because he is that hungry. Yet they were still working, and not only that, it is heard then in the Muslim ranks, they were reciting,
\begin{center}
    \begin{RLtext}
        اللَّهمَّ لولا أنتَ ما اهْتَدَيْنا\\
        ولا تَصَدَّقْنا ولا صَلَّيْنا\\
        فأنْزِلْنَ سَكينةً عَلَيْنا\\
        وثَبِّتِ الأقْدامَ إنْ لاقَيْنا\\
        إنَّ الْأُلى قد بَغَوْا عَلَيْنا\\
    \end{RLtext}
    \textit{O Allah! if it wasn't for you, we wouldn't have been guided.\\
    We wouldn't know salah and we wouldn't know zakah.\\
    So, bestow tranquility upon us.\\
    And make our feet firm, when we meet our enemy.\\
    Indeed, they have transgressed against us.
    }
\end{center}
So, their morale is pretty high. What's their secret? because it's not food, not the equipment, not their situation, nor is it their men. At that stage, they were only 1400 fighting men, and 10,000 plus coming against them. They are on the verge of annihilation, but their belief, confidence, and fearlessness are on such a level that it makes them free from the shackles that everyone else is shackled by.

\subsection*{c. Their Imaan gave them a higher authority to listen to and obey}
Generally, when anyone is judged by a man-made law, there is a feeling of dissatisfaction in the heart. Also, the appropriate submission is not found in it. For example, let's look at divorce, when a divorce takes place by a man-made law, the man on one side says ---The law is like that, it supports women. On the other side, women think ---Men always wrong women. Neither side is happy with the law. Because they don't have a higher power to whom they have internally submitted. 

So, when a situation like this comes, man doesn't know, what to do, or how to judge. Allaah sent them guidance. Then to the law that Allaah rabbul 'izzah sent down, there was full submission from their hearts. So, not only did they follow the law, they self-regulated with the law. For example- In our times, if anyone has a speeding issue, and when over-speeds on a road, will that individual go to the police station and submit his guilt by himself? But when they've reached the law of Allaah, they would go to the Prophet (peace and blessings be upon his soul) ---O Prophet (peace and blessings be upon his soul) of Allaah! I've committed this sin, how do I make amends?\footnote{
    \begin{RLtext}
        عن أبي هريرة رضي الله عنه قال: أَتَى رجل مِنَ المسلمين رسولَ صلى الله عليه وسلم وهو في المسجد فَنَادَاهُ: يا رسول الله، إنِّي زَنَيْتُ، فَأَعْرَضَ عنه، فَتَنَحَّى تِلْقَاءَ وَجْهِهِ فَقَالَ: يا رسول الله، إنِّي زَنَيْت، فأعرض عنه، حَتَّى ثَنَّى ذلك عليه أَرْبَعَ مَرَّاتٍ. فَلَمَّا شَهِدَ عَلَى نَفْسِهِ أَرْبع شهادات: دَعَاهُ رَسُولُ الله صلى الله عليه وسلم ، فَقَالَ: أَبِكَ جُنُونٌ؟ قَالَ: لا، قَالَ: فَهَلْ أُحْصِنْت؟ قَالَ: نَعَمْ، فَقَالَ رَسُولُ الله: اذْهَبُوا بِهِ فَارْجُمُوهُ. قَالَ ابْنُ شِهَابٍ: فَأَخْبَرَنِي أَبُو سَلَمَةَ بنُ عَبْدِ الرَّحْمَنِ. سَمِعَ جَابِرَ بنَ عَبْدِ الله يَقُولُ: كُنْت فِيمَنْ رَجَمَهُ، فَرَجَمْنَاهُ بِالمُصَلَّى، فَلَمَّا أَذْلَقَتْهُ الْحِجَارَةُ هَرَبَ، فَأَدْرَكْنَاهُ بِالحَرَّةِ، فَرَجَمْنَاهُ.  
[صحيح] - [متفق عليه]
    \end{RLtext}
    \textbf{Abu Hurayrah (may Allah be pleased with him) reported: A Muslim man went to the Prophet (may Allah's peace and blessings be upon him) while he was in the mosque and called him, saying: "O Messenger of Allah, I have committed adultery." The Messenger of Allah (may Allah's peace and blessings be upon him) turned his face away from him. So, the man came round (from the other side) towards his face and said: "O Messenger of Allah, I have committed adultery." The Messenger of Allah (may Allah's peace and blessings be upon him) again turned his face away from him, until the man did this four times. When he testified four times that he had done so, the Messenger of Allah (may Allah's peace and blessings be upon him) called him, saying: "Do you suffer any form of insanity?" The man replied: 'No.' The Messenger of Allah (may Allah's peace and blessings be upon him) then asked him: "Are you married?" The man answered: 'Yes.' The Messenger of Allah (may Allah's peace and blessings be upon him) said (to his Companions): "Take him away and stone him (to death)." Ibn Shihāb said: "Abu Salamah ibn ‘Abdur-Rahmān informed me that he heard Jābir ibn ‘Abdullāh say: ‘I was one of those who stoned him. We stoned him at the place of prayer. When the stones hurt him, he ran away. We caught him in Al-Harrah and stoned him (to death).'"}
} And sometimes the consequence would have been capital punishment. A law that they not only followed, but they loved to follow. So they became a society of rules, whereas everyone else is a society of running away from rules. And that is what creates a successful society.


\section*{Allaah rabbul ’izzah changed their minds}
Imaan affected how they used to think. Yesterday they were purposeless, Allaah rabbul 'izaah gave them purpose. Read the chapter \ref{islamAndBeduins}, how Allaah changed the visions of the Bedouins. \\

You can see that, Allaah rabbul 'izzah didn't change their situations, nor did He change their surroundings. He just changed themselves, their insides. Through that, their productivity reached a level that if we compare it with a normal human being, then they will be called superhumans. With that, they conquered East and West. As a result, against all the odds, within a few decades, Islam reached from Granada of Spain to the New Delhi of India. 
}