\chapter{The Ultimate Success}
\textvtt{
We live in an amazing time. Everyone wants success. So we get life courses, we get career courses, we get peer courses, we go to universities and do MBAs, even when our parents sent us to school, they sent us to succeed. Everyone is chasing success but no one seems to know what does success looks like. To a lot of people, success is money and to others it is fame. So, trying to find this elusive success we go back to what our Creator said, and there is no definition better than the one Allaah rabbul 'izzah gave. Listen to what Allaah says,
}
\begin{center}
    \begin{RLtext}
        فَمَن زُحْزِحَ عَنِ ٱلنَّارِ وَأُدْخِلَ ٱلْجَنَّةَ فَقَدْ فَازَ ۗ
    \end{RLtext}
    \textbf{Whoever traverses over Jahannam and enters Jannah that person is indeed successful.} [3:185]
\end{center}
\textvtt{
So success is to live a life that will lead you to Jannah.

Allaah rabbul 'izaah has honored us with a religion, the entire focus of which is success. You can't deny that. Five times a day you hear the screamer calls at the top of his lungs,
}
\begin{center}
    \begin{RLtext}
        حَيَّ عَلَىٰ ٱلْفَلَاحِ
    \end{RLtext}
    \textbf{Come towards success}.
\end{center}
\textvtt{
There's no other system on the face of this earth, where a man calls five times a day ---come to success. And if you study in-depth every aspect of the \textit{deen}, it is designed to make you successful not only in the hereafter but in this life as well.

The psychologists say that--- the most productive emotion is the emotion of gratitude. In your heart, if you feel grateful, you will be very productive. You will be at the top of your game, you'll be at your best.

The successful people, as in people who are the heads of industries, CEOs, enterprenuours ---successful by the definitions of men, they are people who remembers the favours in their life as soon as they wake up early in the morning keeping their eyes closed for a couple of minutes. They have discovered this now in the 2000s, to be grateful.

Let's look at our \textit{deen}, the \textit{deen} of Muhammad the best of blessings be upon his soul. We know that the Messenger of Allah and His companions had a very tough life most of the time with a very limited provisions. Yet when they used to wake up they used to say,
}
\begin{center}
    \begin{RLtext}
    اَلْحَمْدُ لِلّٰهِ الَّذِيْ أَحْيَانَا بَعْدَ مَا أَمَاتَنَا، وَإِلَيْهِ النُّشُوْرُ
    \end{RLtext}
    \textbf{“All praise is for Allaah who gave us life after having taken it from us and unto Him is the resurrection”} [Al-Bukhari]
\end{center}
\textvtt{
And if we focus the daily routine of our Beloved, we would notice that every single act someway or the other He thanked \textit{Rabbul 'izzati wal jalaal}. His whole life was full of gratitude.

If we research those man defined successful men's life we would also find certain traits. They are all early raisers, almost between 4:00-6:00 AM. Although work starts at 9:00 AM usually. They wake up and meditate, or they read motivational texts, to inspire them for the rest of the day.

What did the \textit{deen} of Allaah prescribed to do in the early morning? We stand in \textit{salah}, and we know that \textit{Fazr} is of long recitations, of the most motivational text man is ever to know, the devine word of Almighty Himself. Then we supposed to sit and do our morning \textit{adhkar}. It takes normally 20 to 30 minutes to complete the whole morning \textit{adhkar}. I can sware by Allaah ---if anyone starts his day as your Rabb wants to start, by the time he goes to his work his heart would be dancing. Why? Because the \textit{deen} was made to give you the best of this life and the next.

\section*{The Story of 'Aamir Ibnu Fuhairah}
I want to conclude this chapter by the following story of a man who lived his life in the obedience of Allaah and the obedience of the Rasul peace be upon him. His name is 'Aamir Ibnu Fuhairah may Allaah be pleased with him. He was the freed slave of Abi Bakr as-Siddique may Allaah be pleased with him. Though he was freed, but as he was loyal, he stayed with Abi Bakr may Allaah be pleased with him and served the \textit{deen}.

At the time of \textit{hijrah} of the Prophet peace and blessings be upon him, 'Aamir Ibn Fuhairah stood firm. He was one of the very few who knew that the Prophet is migrating. He was the one who went and got the camels, he was the one that took food to the mountain when the Prophet peace be upon him and Abi Bakr was in \textit{Ghar-e-thaur}, he was the one that brought 'Abdullah Ibn 'Uraiqit to them. In short, he was the person standing in this difficulty with them. Allaah blessed them to migrate with the Messenger of Allaah.

Years passed, 'Aamir is in \textit{Madina}, safety and security has been established in \textit{Madina}. Through his closeness to the Messenger of Allaah, closeness to the companions and his obedience to Allaah and His Prophet, he has now become one of the most learned of Muslims. Then one day a leader of a tribe came from outside of \textit{Madina} to the Prophet of Allaah and asked, "O Prophet of Allaah! can you send us some teachers to teach my people the \textit{deen} of Allaah?" So the Prophet of Allaah sent teachers (\textit{ashaab}) to go and teach the new Muslims. Amidst the group is 'Amr Ibn Fuhairah may Allaah be pleased with him. As they were travelling, on the way they camped at night/afternoon. As they camped, the get ambushed. The enemy killed all of them at the camp mercylessly. Two or three of the companions went out of the camp to graze the animal. When they returned, they saw massacre. They reacted, screemed run to their brother's deadbodies but the enemy caught them and tied them up. One of them screemed, "Let me go and I'll show you what I'll do". They said, "What will you do?" He said, "I'll fight again". They released him, he fights again, they tied him up again. They've already killed everyone else. But now no one wants to kill these two. They are just tying them up. It's a strange situation. Then the enemy showed them all the deadbodies and then asked them, "Is there anyone missing?" They said, "Yes, there's one person missing". They asked, "Who is he?" They replied, "'Amr Ibnu Fuhairah". They asked, "Who was he amidst you?" They replied, "The best of us [Early Muslim, migrant, helper of the Prophet peace be upon him]". Then the enemy took them to a man who was dazed, just looking out blank. His name was Jabbaar. They said, "This is Jabbar. Jabbar! Tell them what happened". Jabbar said, "I came from behind him ('Amr Ibn Fuhairah), I got my spear. Then I dug it in his back and the blade came out from his chest". The normal reaction that Jabbaar anticipated that, screem, agony. But when 'Amr Ibnu Fuhairah looked that blade has come out from his chest, he smiled and said,   
\begin{center}
    \begin{RLtext}
        فزتو ورب الكعبة
    \end{RLtext}
    \textit{I succeeded by the Lord of the Ka'aba}
\end{center}
Jabbaar said, "I pulled the blade out, and thought that maybe I've missed him. Then when I wanted to stab him again he started to went up until he disapeared in the clouds". Listening to Jabbaar the companions said, "The angels took him up".

'Amir Ibnu Fuhairah may Allaah be pleased with him lived a life in the obedience of Allaah and the obedience of the Rasul, then when death came and however it came, he was successful. Allaah \textit{Rabbul 'izaah} says,
}
\begin{center}
    \begin{RLtext}
        وَمَن يُطِعِ ٱللَّهَ وَرَسُولَهُۥ فَقَدْ فَازَ فَوْزًا عَظِيمًا 
    \end{RLtext}
    \textbf{And whoever obeys Allāh and His Messenger has certainly attained a great attainment.} [33:71]
\end{center}
\textvtt{
He also says,
}
\begin{center}
    \begin{RLtext}
        مَّن يُصْرَفْ عَنْهُ يَوْمَئِذٍ فَقَدْ رَحِمَهُۥۚ وَذَٰلِكَ ٱلْفَوْزُ ٱلْمُبِينُ 
    \end{RLtext}
    \textbf{He from whom it is averted that Day - [Allāh] has granted him mercy. And that is the clear attainment.} [6:16]
\end{center}
